The function--sheaf dictionary for smooth commutative group schemes over finite fields

### 2014-08-06 dictionary.tex
Adding short section on automorphisms

>>>>

\todo{Find an appropriate place for this discussion}

If $\rho_0 = 0$ then the second diagram for $y=0$ implies that $\rho_x = 0$ for all $x$.  Conversely, if $\rho_0$ is nonzero then the second diagram for $y = -x$ implies that $\rho_x$ is nonzero for all $x$ and thus an isomorphism since $\gqcs{L}_x$ is one dimensional.  Most of this paper focuses on the question of determining the isomorphism classes of objects; a complete understanding of the morphisms in $\rQC(G)$ also requires a description of the automorphisms of an arbitrary quasicharacter sheaf $\qcs{L}$.

\begin{proposition}
The trace map induces an isomorphism of groups
\[
\Aut(\qcs{L}) \cong \Hom(G(\bFq)_{\Weil{}}, \EEx).
\]
\end{proposition}

\begin{proof}
The second diagram in \ref{qc.4} shows that the association $x \mapsto \rho_x$ is a homomorphism from $G(\bFq)$ to $\EEx$ and the first shows that it factors through $G(\bFq)_{\Weil{}}$.  Conversely, if $\rho : G(\bFq)_{\Weil{}} \to \EEx$ is any homomorphism then defining $\rho_x$ as multiplication by $\rho(x)$ will satisfy the two diagrams.  Composition of morphisms corresponds to pointwise multiplication in this correspondence, showing that the resulting bijection is actually a group ismorphism.
\end{proof}
